\section{Experience}
\outerlist{
    \entrybig
        {\textbf{Senior Backend Software Developer}}{Toronto, ON}
        {Scotia Digital \textendash{ }Scotiabank}{June 2022 \textendash{ }Present}
    \innerlist{
        \entry{Reduced response times of a core product by over 60\% by implementing several API optimizations, including response compression, parallel processing, and data prefetching.}
        \entry{Revamped and enriched project documentation, alleviating a significant pain point in the onboarding process for new team members.}
        \entry{Led the design and development of a high-impact cross-functional project, streamlining workflows and reducing manual tasks for teams across departments.}
        \entry{Collaborated with product managers to ideate and craft project features based on user feedback.}
    }
    \entrybig
        {\textbf{Senior Software Developer}}{Toronto, ON}
        {Royal Bank of Canada}{August 2020 \textendash{ }June 2022}
    \innerlist{
        \entry{Supervised and provided project direction to co-op students, junior team members, and offshore contractors.}
        \entry{Designed and developed cohesive end-to-end processes connecting multiple applications and organizations to minimize manual tasks in financial operations.}
        \entry{Worked closely and continuously with clients to outline requirements, develop user stories, and steer project direction.}
    }

    \entrybig
        {\textbf{Software Developer}}{Toronto, ON}
        {Royal Bank of Canada}{January 2018 \textendash{ }August 2020}
    \innerlist{
        \entry{Designed and developed robust ETL applications using .NET Core to replace antiquated manual processes.}
        \entry{Developed and maintained both server-side and desktop Java applications to automate manual processes, saving hundreds of human-hours per week.}
        \entry{Automated a resource-intensive manual hygiene process, significantly reducing the impact to production resources and saving approximately 20 human-hours per week.}
        \entry{Supported and maintained an enterprise application that facilitates millions of transactions everyday.}
    }

    \entrybig
        {\textbf{Technical Systems Analyst Co-op (Mainframe Operations)}}{Toronto, ON}
        {Royal Bank of Canada}{May 2017 \textendash{ }August 2017}
    \innerlist{
        \entry{Rolled out upgrades to mainframe system utilities across multiple environments.}
    }

    \entrybig
        {\textbf{Database Developer Co-op}}{Mississauga, ON}
        {Bond Brand Loyalty}{January 2016 \textendash{ }December 2016}
    \innerlist{
        \entry{Developed efficient stored procedures, functions, and SQL queries to fit growing business needs and fulfill client requests.}
    }
}
